### 2019-06-27 report/MSc_Report.tex
Results update

\chapter{The Cochrane Dataset}

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Mon Jun 17 16:15:38 2019
\begin{table}[ht]
\centering
\begingroup\scriptsize
\begin{tabular}{lllrrrr}
  \hline
Study & Comparison & Outcome & Events & Total & Events\_c & Total\_c \\ 
  \hline
Bohn 1989 & Barbiturate vs no barbiturate & Death at the end of follow-up & 11 & 41 & 11 & 41 \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Death at the end of follow-up & 14 & 27 & 13 & 26 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Example of two results as given in the dataset. Events denotes the count of events in the treatment group while Events c the count of events in the group compared to. Further descriptive variables have been ommitted} 
\label{barbiturate.row}
\end{table}

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Mon Jun 17 16:15:38 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lll}
  \hline
Study & Comparison & Outcome \\ 
  \hline
Bohn 1989 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
  Bohn 1989 & Barbiturate vs no barbiturate & Death or severe disability at the end of follow-up \\ 
  Eisenberg 1988 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
  Eisenberg 1988 & Barbiturate vs no barbiturate & Uncontrolled ICP during treatment \\ 
  Eisenberg 1988 & Barbiturate vs no barbiturate & Hypotension during treatment \\ 
  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Death at the end of follow-up (6 months) \\ 
  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Death or severe disability at the end of follow-up (6 months) \\ 
  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Uncontrolled ICP during treatment \\ 
  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Hypotension during treatment \\ 
  Schwartz 1984 & Barbiturate vs Mannitol & Death at the end of follow-up (1 year) \\ 
  Schwartz 1984 & Barbiturate vs Mannitol & Death at the end of follow-up (1 year) \\ 
  Schwartz 1984 & Barbiturate vs Mannitol & Uncontrolled ICP during treatment \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Death or severe disability at the end of follow-up \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Mean ICP during treatment \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Mean arterial pressure during treatment \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Hypotension during treatment \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Mean body temperature during treatment \\ 
   \hline
\end{tabular}
\endgroup
\caption{Barbiturate and head injury review. In the columns, study names, comparison and outcome measure of the results are given} 
\label{barbiturates}
\end{table}

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Mon Jun 17 16:15:38 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lr}
  \hline
  \hline
Missing mean values and mean differences & 984 \\ 
  Missing standard deviations and standard errors & 1300 \\ 
  Missing sample sizes & 12173 \\ 
  Missing study year & 44649 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Number of missing variables and measurements in the dataset} 
\label{missing}
\end{table}

The studies that are included in the reviews and have been published are most often from the years after 1980 (5\% quantile = 1982). The median of the publication years is 2003, the mean 2001 and the quartiles are 1996 and 2008. Only a handful ($n = 18$) have been published in 2018, none in 2019. \\
%No information is available concerning unpublished results and studies.
The top treatment effect measure (risk ratio, mean difference, hazard ratio etc.) abundances are summarized in Table \ref{outcome.measure.frequencies}. One can conclude of the table that roughly 30 \% of outcomes in the dataset are continuous and the rest being some sort of discrete or binary outcomes, most often binary (> 65\%).

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Mon Jun 17 16:15:38 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lll}
  \hline
Outcome measure & n & Percentage \\ 
  \hline
Risk Ratio & 232583 & 50.1\% \\ 
  Mean Difference & 102315 & 22.1\% \\ 
  Odds Ratio & 49372 & 10.6\% \\ 
  Std. Mean Difference & 40535 & 8.7\% \\ 
  Peto Odds Ratio & 19122 & 4.1\% \\ 
  Hazard Ratio & 6566 & 1.4\% \\ 
  Risk Difference & 6234 & 1.3\% \\ 
  Rate Ratio & 2283 & 0.5\% \\ 
  other & 4810 & 1\% \\ 
   \hline
\end{tabular}
\endgroup
\caption{Frequencies of outcome measures among results. n denotes the total number 
             of results with the outcome measure and percentage the percentage of the outcome measure,} 
\label{outcome.measure.frequencies}
\end{table}

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Mon Jun 17 16:15:38 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lll}
  \hline
n & Number of groups & Cumulative sum of groups \\ 
  \hline
1 & 102344 & 186300 \\ 
  2 & 31686 & 83956 \\ 
  3 & 16072 & 52270 \\ 
  4 & 9628 & 36198 \\ 
  5 & 6444 & 26570 \\ 
  6 & 4230 & 20126 \\ 
  7 & 2961 & 15896 \\ 
  8 & 2114 & 12935 \\ 
  9 & 1592 & 10821 \\ 
  10 & 1238 & 9229 \\ 
  11 & 921 & 7991 \\ 
  12 & 702 & 7070 \\ 
  13 & 585 & 6368 \\ 
  14 & 455 & 5783 \\ 
  15 & 5328 & 5328 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Cumulative number of groups with number of reproduction trials >= n} 
\label{repr.groups}
\end{table}

@@

\chapter{Results}

@@

The results of the test for small study effects and excess of significance for the meta-analyses fullfilling the criteria from chapter \ref{chapter02}, section \ref{sec:Processing}, are presented in Figure \ref{fig:test}.
%Figures \ref{fig:test.bin}, \ref{fig:test.cont} and \ref{fig:test.surv}. 
The histogram of the $p$-values is displayed separately for binary, continuous and survival outcome types (as previously defined in the dataset variable \texttt{outcome.type}, see chapter \ref{ch:chapter02}, section \ref{sec:Processing}. The distributions are (with the exception of Schwarzer's test) skewed to the right, indicating evidence for small study effects. Moreover, the excess significance tests have a mode around $p = 0.4$. Large differences between small study effect tests for binary and continuous outcomes will be subject to discussion. \\
``Excess significance'' denotes the excess of significance $p$-values from the test of \citet{excess.significance}. For continuous and survival outcomes, the names refer to:

@@

\begin{figure}[ht!]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}

@@

The agreement/coinicidence between between small study effect and excess significance tests is often not pronounced, thus, it will be compared by different methods. This is displayed in Table \ref{test.agreement}. The row names indicate which two tests are compared. First, the column ``Test Agreement'' quantifies the overall proportion by which the two tests agree in their rejection or ``acceptance'' of the null-hypothesis. ``Test Agreement'' being equal one thus indicates equivalent results, zero no correspondence whatsoever. The second column, ``Correlation'' gives the correlation between the $p$-values. A positive correlation indicates psotive coincidence of $p$-values, negative correlation coincidence in opposite directions. However, the scale might be different for this agreement measure. The ``R-squared'' value indicates to what extent one $p$-value can be predicted by another, and ignores additive differences between $p$-values (as for correlation), as well as multiplicative constants between them (i.e. $y ~ a + b*x$, $y$ and $x$ being two $p$-values of test-statistics). An R-squared value of 1 indicates perfect fit. Importantly, the order of the variables does not matter for the $p$-values for all indicators (i.e. $p$-values for $x$ and $y$ can be exchanged and the table stays the same). If a test is completely replaceable by another, all values in a row are equal to one.

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Mon Jun 24 17:05:43 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lccc}
  & Test Agreement & p-value Correlation & p-value R-squared \\ 
  \hline
\hline
Excess significance, Schwarzer & 0.83 & -0.02 & 0.00 \\ 
  Excess significance, Peter & 0.80 & 0.05 & 0.00 \\ 
  Excess significance, Rucker & 0.82 & 0.12 & 0.02 \\ 
  Excess significance, Harbord & 0.81 & 0.02 & 0.00 \\ 
  Peter, Schwarzer & 0.82 & 0.29 & 0.09 \\ 
  Schwarzer, Rucker & 0.82 & 0.29 & 0.08 \\ 
  Schwarzer, Harbord & 0.86 & 0.51 & 0.26 \\ 
  Rucker, Peter & 0.89 & 0.64 & 0.41 \\ 
  Harbord, Peter & 0.86 & 0.48 & 0.23 \\ 
   \hline
Excess significance, Egger & 0.79 & 0.14 & 0.02 \\ 
  Excess significance, Thompson & 0.80 & 0.16 & 0.02 \\ 
  Excess significance, Begg & 0.81 & 0.10 & 0.01 \\ 
  Thompson, Egger & 0.95 & 0.91 & 0.83 \\ 
  Thompson, Begg & 0.87 & 0.70 & 0.49 \\ 
  Egger, Begg & 0.86 & 0.65 & 0.42 \\ 
   \hline
Excess significance, Egger (survival) & 0.69 & 0.03 & 0.00 \\ 
  Excess significance, Thompson (survival) & 0.64 & 0.05 & 0.00 \\ 
  Excess significance, Begg (survival) & 0.62 & 0.18 & 0.03 \\ 
  Thompson, Egger (survival) & 0.90 & 0.92 & 0.85 \\ 
  Thompson, Begg (survival) & 0.92 & 0.66 & 0.43 \\ 
  Egger, Begg (survival) & 0.87 & 0.70 & 0.48 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Agreement in significance proportion, correlation and R-squared of linear regression
             between the p-values of the publication bias tests. Horizontal lines separate binary, continuous and survival outcomes (order as in table).} 
\label{test.agreement}
\end{table}

@@

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-13-1}

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Mon Jun 24 17:05:45 2019
\begin{table}[ht]
\centering
\begingroup\tiny
\begin{tabular}{lcccrrrrrrrr}
  \hline
meta.id & file.nr & comparison.nr & subgroup.nr & z fixed & z random & z Copas & z regression & g fixed & g random & g Copas & g regression \\ 
  \hline
2009 & 2009 & 1 & 1 & 0.31 & 0.36 & 0.31 & 0.43 & 0.70 & 0.70 & 0.70 & 2.48 \\ 
  2068 & 2068 & 2 & 0 & 0.29 & 0.35 & 0.29 & 0.43 & 0.68 & 0.68 & 0.68 & 2.57 \\ 
  18658 & 18658 & 2 & 0 & 1.16 & 1.14 & 1.16 & 1.17 & 1.40 & 2.85 & 1.40 & 1.74 \\ 
  46472 & 46472 & 1 & 1 & 1.79 & 1.44 & 1.79 & 0.66 & 0.12 & 6.97 & 6.97 & 0.79 \\ 
  52528 & 52528 & 1 & 0 & -0.75 & -0.69 & -0.50 & -0.26 & -1.19 & -1.53 & 0.18 & -0.52 \\ 
  60546 & 60546 & 1 & 1 & 0.17 & 0.24 & 0.17 & 0.34 & 0.53 & 0.53 & 0.53 & 1.65 \\ 
  70389 & 70389 & 1 & 1 & -0.08 & -0.07 & 15.58 & -0.04 & -0.13 & -0.13 & -0.13 & -0.05 \\ 
  73769 & 73769 & 3 & 1 & -0.14 & 0.00 & 214760.42 & -0.04 & -0.01 & -0.12 & 0.01 & 0.04 \\ 
  79113 & 79113 & 2 & 0 & -0.38 & -0.38 & -0.38 & -0.48 & -0.93 & -0.93 & -2.00 & -3.47 \\ 
  90138 & 90138 & 3 & 0 & 0.31 & 0.80 & 0.31 & 0.55 & 0.72 & 0.71 & 0.71 & 2.16 \\ 
  97356 & 97356 & 2 & 0 & -0.08 & -0.33 & -0.08 & -0.17 & -0.42 & -0.35 & -1.58 & -1.82 \\ 
  98030 & 98030 & 1 & 0 & -0.09 & -0.07 & -0.09 & -0.04 & -0.41 & -0.41 & -1.50 & -2.79 \\ 
  101436 & 101436 & 1 & 5 & 0.54 & 0.62 & 0.80 & 0.91 & 1.21 & 1.21 & 1.21 & 2.74 \\ 
  118121 & 118121 & 4 & 1 & 0.25 & 0.23 & 71.80 & -0.03 & 0.44 & 0.44 & 0.44 & 0.14 \\ 
  119537 & 119537 & 3 & 0 & 0.07 & 0.15 & 0.07 & 0.29 & 0.50 & 0.50 & 1.43 & 1.81 \\ 
  119818 & 119818 & 3 & 3 & -0.25 & -0.25 & -0.11 & -0.04 & -0.50 & -0.54 & 28.44 & -0.03 \\ 
  146301 & 146301 & 1 & 0 & 0.14 & 0.26 & 498188.34 & 0.28 & 0.56 & 0.37 & 0.60 & 0.52 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Missing meta-analysis pooled treatment effect and adjusted treatment effects
             of Figure 
ef{fig:adjustment.size}. Abbreviations are used for z-score (z) and Hedges g (g)} 
\label{missing.differences}
\end{table}

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Mon Jun 24 17:05:45 2019
\begin{table}[ht]
\centering
\begingroup\scriptsize
\begin{tabular}{lcccccc}
  \hline
 & 5\% & 25\% & 50\% & 75\% & 95\% & mean \\ 
  \hline
z-score: Fixed - Copas & -0.05 & -0.01 & 0.00 & 0.01 & 0.05 & 402.37 \\ 
  z-score: Random - Copas & -0.04 & 0.00 & 0.00 & 0.00 & 0.01 & 159.98 \\ 
  z-score: Fixed - Regression & -0.15 & -0.05 & -0.01 & 0.04 & 0.13 & -0.01 \\ 
  z-score: Random - Regression & -0.18 & -0.07 & -0.02 & 0.03 & 0.16 & -0.02 \\ 
  Hedges g: Fixed - Copas & -0.09 & -0.01 & 0.00 & 0.01 & 0.05 & -0.02 \\ 
  Hedges g: Random - Copas & -0.14 & 0.00 & 0.00 & 0.00 & 0.00 & -0.04 \\ 
  Hedges g: Fixed - Regression & -0.39 & -0.13 & -0.04 & 0.04 & 0.24 & -0.05 \\ 
  Hedges g: Random - Regression & -0.43 & -0.17 & -0.05 & 0.03 & 0.23 & -0.07 \\ 
  Log hazard ratio: Fixed - Copas & -0.02 & -0.00 & 0.00 & 0.00 & 0.03 & 0.01 \\ 
  Log hazard ratio: Random - Copas & -0.00 & 0.00 & 0.00 & 0.00 & 0.03 & 0.01 \\ 
  Log hazard ratio: Fixed - Regression & -0.15 & -0.01 & 0.07 & 0.14 & 0.21 & 0.06 \\ 
  Log hazard ratio: Random - Regression & -0.15 & -0.03 & 0.07 & 0.15 & 0.23 & 0.06 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Quantiles and Means of the differences between meta-analysis pooled treatment effects and small study adjusted treatment effects. The row names indicate which outcome measure, meta-analysis and adjustment method is used} 
\label{adjustment.difference}
\end{table}

@@

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-16-1}

@@

>>>>

\chapter{The Cochrane Dataset} \label{ch:dataset}

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Thu Jun 27 15:14:56 2019
\begin{table}[ht]
\centering
\begingroup\scriptsize
\begin{tabular}{lllrrrr}
  \hline
Study & Comparison & Outcome & Events & Total & Events\_c & Total\_c \\ 
  \hline
Bohn 1989 & Barbiturate vs no barbiturate & Death at the end of follow-up & 11 & 41 & 11 & 41 \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Death at the end of follow-up & 14 & 27 & 13 & 26 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Example of two results as given in the dataset. Events denotes the count of events in the treatment group while Events c the count of events in the group compared to. Further descriptive variables have been ommitted} 
\label{barbiturate.row}
\end{table}

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Thu Jun 27 15:14:57 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lll}
  \hline
Study & Comparison & Outcome \\ 
  \hline
Bohn 1989 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
  Bohn 1989 & Barbiturate vs no barbiturate & Death or severe disability at the end of follow-up \\ 
  Eisenberg 1988 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
  Eisenberg 1988 & Barbiturate vs no barbiturate & Uncontrolled ICP during treatment \\ 
  Eisenberg 1988 & Barbiturate vs no barbiturate & Hypotension during treatment \\ 
  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Death at the end of follow-up (6 months) \\ 
  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Death or severe disability at the end of follow-up (6 months) \\ 
  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Uncontrolled ICP during treatment \\ 
  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Hypotension during treatment \\ 
  Schwartz 1984 & Barbiturate vs Mannitol & Death at the end of follow-up (1 year) \\ 
  Schwartz 1984 & Barbiturate vs Mannitol & Death at the end of follow-up (1 year) \\ 
  Schwartz 1984 & Barbiturate vs Mannitol & Uncontrolled ICP during treatment \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Death or severe disability at the end of follow-up \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Mean ICP during treatment \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Mean arterial pressure during treatment \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Hypotension during treatment \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Mean body temperature during treatment \\ 
   \hline
\end{tabular}
\endgroup
\caption{Barbiturate and head injury review. In the columns, study names, comparison and outcome measure of the results are given} 
\label{barbiturates}
\end{table}

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Thu Jun 27 15:14:57 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lr}
  \hline
  \hline
Missing mean values and mean differences & 984 \\ 
  Missing standard deviations and standard errors & 1300 \\ 
  Missing sample sizes & 12173 \\ 
  Missing study year & 44649 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Number of missing variables and measurements in the dataset} 
\label{missing}
\end{table}

The studies that are included in the reviews and have been published are most often from the years after 1980 (5\% quantile = 1983). The median of the publication years is 2003, the mean 2001.03 and the quartiles are 1996 and 2008. Only a handful ($n = 18$) have been published in 2018, none in 2019. \\
%No information is available concerning unpublished results and studies.
The top treatment effect measure (risk ratio, mean difference, hazard ratio etc.) abundances are summarized in Table \ref{outcome.measure.frequencies}. One can conclude of the table that roughly 30 \% of outcomes in the dataset are continuous and the rest being some sort of discrete or binary outcomes, most often binary (> 65\%).

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Thu Jun 27 15:14:57 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lll}
  \hline
Outcome measure & n & Percentage \\ 
  \hline
Risk Ratio & 232583 & 50.1\% \\ 
  Mean Difference & 102315 & 22.1\% \\ 
  Odds Ratio & 49372 & 10.6\% \\ 
  Std. Mean Difference & 40535 & 8.7\% \\ 
  Peto Odds Ratio & 19122 & 4.1\% \\ 
  Hazard Ratio & 6566 & 1.4\% \\ 
  Risk Difference & 6234 & 1.3\% \\ 
  Rate Ratio & 2283 & 0.5\% \\ 
  other & 4810 & 1\% \\ 
   \hline
\end{tabular}
\endgroup
\caption{Frequencies of outcome measures among results. n denotes the total number 
             of results with the outcome measure and percentage the percentage of the outcome measure,} 
\label{outcome.measure.frequencies}
\end{table}

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Thu Jun 27 15:14:57 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lll}
  \hline
n & Number of groups & Cumulative sum of groups \\ 
  \hline
1 & 102344 & 186300 \\ 
  2 & 31686 & 83956 \\ 
  3 & 16072 & 52270 \\ 
  4 & 9628 & 36198 \\ 
  5 & 6444 & 26570 \\ 
  6 & 4230 & 20126 \\ 
  7 & 2961 & 15896 \\ 
  8 & 2114 & 12935 \\ 
  9 & 1592 & 10821 \\ 
  10 & 1238 & 9229 \\ 
  11 & 921 & 7991 \\ 
  12 & 702 & 7070 \\ 
  13 & 585 & 6368 \\ 
  14 & 455 & 5783 \\ 
  15 & 5328 & 5328 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Cumulative number of groups with number of reproduction trials >= n} 
\label{repr.groups}
\end{table}

@@

\chapter{Results} \label{ch:Results}

@@

The meta-analyses fullfilling the criteria from chapter \ref{ch:dataset}, section \ref{sec:Processing}, are analysed with small study effects tests and excess significance tests. The $p$-values for all meta-analyses can be displayed in histograms. Because the tests are methodologically different, the results of each testing method is displayed separately. Furthermore, the outcome types (as defined previously by the variable \texttt{outcome.type}) are also kept separated.\\
The histograms in Figure \ref{fig:test} show that the distributions are (with the exception of Schwarzer's test) skewed to the right for all outcome types, indicating evidence for small study effects and excess significance. Moreover, the excess significance tests have a mode around $p = 0.4$. The large differences between small study effect tests for binary and continuous outcomes will be subject to discussion.\\
``Excess significance'' denotes the excess of significance $p$-values from the test of \citet{excess.significance}, see \ref{sex:excess.significance}. For continuous and survival outcomes, the names refer to:

@@

@@

%Agreement table -> Chunck 1

It cannot be seen in Figure \ref{fig:test} if the tests used are finding small study effects/excess significance for the same meta-analyses. Especially between small study effects and excess significance tests, we expect some disagreement between tests. A simple method to check the coincidence of test results is to compare scatterplots and empirical spearman correlations between test statistics. This is done in Figure \ref{fig:test.agreement}. \\
Here, there is no separation between survival and continuous outcomes. The upper left rectangle is displaying binary outcomes and the lower right about continuous and survival outcomes.

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-11-1}

\end{knitrout}
\caption{Pairs-plot for test statistics of small study effect and excess significance. The lower panel gives the spearman correlations for the different test statistics, and the upper panel displays a scatterplot. The colours indicate magnitude and direction of the correlation coefficients. The rectangle with white borders displays the area within which both tests have absolute value < 1.96.}
\label{fig:test.agreement}
\end{figure}

The observed patterns on the scatterplots differ: Excess significance and small study effect test statistics do usually not align with each other, forming rather randomly scattered bulks of points. Regression based tests as Egger and Thompson which are methodically almost identical are closely aligned, which is also reflected in large correlation coefficients. In general, small study effect tests align, but the extent to which they align differs. Harbord's test statistic has similar correlation coefficients with all other small study effect test statistics for binary outcomes, while the correlation coefficients between them is varying.\\
Because scatterplots and correlation coefficients can be missleading, also a Tukey mean-difference or Bland-Altmann plot is shown for three scenarios in Figure \ref{fig:mean.diff.test}:
\begin{itemize}
\item For Egger's and Thompson's tests, which is supposedly the most similar test and should show the least deviations and systematic errors
\item For Harbord's and Rucker's tests
\item For Harbord's and excess significance tests
\end{itemize}

This can be justified since all tests are supposed to measure the evidence for publication bias. For the plots, the $p$-values of the tests are transformed on the entire continuous scale by a logit transformation. The mean $p$-value ((logit($p$-value 1) + logit($p$-value 2))/2) is then displayed against the differnec between the $p$-value. If no systematic errors and biases exist between the measurement methods, then

\begin{itemize}
\item the mean of the differences (systematic error) should be around zero
\item the points should scatter independent of the mean of the $p$-values
\end{itemize}

The last criterium seems not to be given when comparing Harbords and Excess significance tests. 
-- In the appendix, it can be seen that this is reproducible with the remainig small study effect tests (not there yet) -- 
With decreasing mean, the difference gets more negative, and vice versa, such that one would predict that the excess significance $p$-values are more ``extreme'' in both directions. This finding suggests that correspondence between the tests is poor. The confidence intervals can be used as limits of agreement, which gives, after back-transformation, around 0.9 for Egger and Thompson test, and around 0.99 for Harbord and Rucker.

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-12-1}

\end{knitrout}
\caption{Mean - difference plots for logit transformed $p$-values. The mean of logit transformed $p$-values is displayed on the $x$-axis and the difference on the $y$-axis. Blue and red lines display the systematic error and the confidence intervals of the systematic error (limits of agreement).}
\label{fig:mean.diff.test}
\end{figure}

The previous results suggest that the results will also differ substantially after applying the common dichotomization of $p$-values. We expect that some proportion of the meta-analysis will only be significant for a certain test, and this is indeed observed in Table \ref{number.sig.tests}. It displays the percentage of meta-analyses with a certain number of significant test results.

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Thu Jun 27 15:14:57 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{ccc}
  \hline
Count & Binary Outcomes & Continuous and Survival \\ 
  \hline
  0 & 65.9 \% & 68.4 \% \\ 
    1 & 16.4 \% & 9.6 \% \\ 
    2 & 8.6 \% & 9.1 \% \\ 
    3 & 5.6 \% & 10.6 \% \\ 
    4 & 2.9 \% & 2.3 \% \\ 
    5 & 0.6 \% & NA \% \\ 
   \hline
\end{tabular}
\endgroup
\caption{Counts Number of significant test results per meta-analysis, separated
       for outcome types. Last entry for continuous and survival outcomes is empty since one test less was 
       applied} 
\label{number.sig.tests}
\end{table}

When only looking at small study effect tests, 29.1\% of binary outcome tests and 26.5\% of survival and continuous outcome tests had at least one significant result. After applying the bonferroni correction for multiple testing, this shrinks to 10.9\& for binary and 12.1\% for continuous and survival outcomes. \\
When comparing significant findings for small study effect tests and excess significance tests, we will only do so with Harbord's or Egger's test. 22.4\% of binary outcome analyses had at least one of the two test $p$-values being significant, and equivalently, 28\% for continuous and survival outcomes. Again, the numbers change to 13.3\% for binary outcomes and 17.2\% for continuous and survival outcomes after applying the bonferroni correction. \\
3\% have significant Harbord's test result and significant excesss significance test result  (1.1\% with bonferroni). Of the continuous outcomes, we have 6.1 \% with Egger's test and 1.8 with Bonferroni correction.

@@

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-15-1}

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Thu Jun 27 15:12:39 2019
\begin{table}[ht]
\centering
\begingroup\tiny
\begin{tabular}{lcccrrrrrrrr}
  \hline
meta.id & file.nr & comparison.nr & subgroup.nr & z fixed & z random & z Copas & z regression & g fixed & g random & g Copas & g regression \\ 
  \hline
2009 & 2009 & 1 & 1 & 0.31 & 0.36 & 0.31 & 0.43 & 0.70 & 0.70 & 0.70 & 2.48 \\ 
  2068 & 2068 & 2 & 0 & 0.29 & 0.35 & 0.29 & 0.43 & 0.68 & 0.68 & 0.68 & 2.57 \\ 
  18658 & 18658 & 2 & 0 & 1.16 & 1.14 & 1.16 & 1.17 & 1.40 & 2.85 & 1.40 & 1.74 \\ 
  46472 & 46472 & 1 & 1 & 1.79 & 1.44 & 1.79 & 0.66 & 0.12 & 6.97 & 6.97 & 0.79 \\ 
  52528 & 52528 & 1 & 0 & -0.75 & -0.69 & -0.50 & -0.26 & -1.19 & -1.53 & 0.18 & -0.52 \\ 
  60546 & 60546 & 1 & 1 & 0.17 & 0.24 & 0.17 & 0.34 & 0.53 & 0.53 & 0.53 & 1.65 \\ 
  70389 & 70389 & 1 & 1 & -0.08 & -0.07 & 15.58 & -0.04 & -0.13 & -0.13 & -0.13 & -0.05 \\ 
  73769 & 73769 & 3 & 1 & -0.14 & 0.00 & 214760.42 & -0.04 & -0.01 & -0.12 & 0.01 & 0.04 \\ 
  79113 & 79113 & 2 & 0 & -0.38 & -0.38 & -0.38 & -0.48 & -0.93 & -0.93 & -2.00 & -3.47 \\ 
  90138 & 90138 & 3 & 0 & 0.31 & 0.80 & 0.31 & 0.55 & 0.72 & 0.71 & 0.71 & 2.16 \\ 
  97356 & 97356 & 2 & 0 & -0.08 & -0.33 & -0.08 & -0.17 & -0.42 & -0.35 & -1.58 & -1.82 \\ 
  98030 & 98030 & 1 & 0 & -0.09 & -0.07 & -0.09 & -0.04 & -0.41 & -0.41 & -1.50 & -2.79 \\ 
  101436 & 101436 & 1 & 5 & 0.54 & 0.62 & 0.80 & 0.91 & 1.21 & 1.21 & 1.21 & 2.74 \\ 
  118121 & 118121 & 4 & 1 & 0.25 & 0.23 & 71.80 & -0.03 & 0.44 & 0.44 & 0.44 & 0.14 \\ 
  119537 & 119537 & 3 & 0 & 0.07 & 0.15 & 0.07 & 0.29 & 0.50 & 0.50 & 1.43 & 1.81 \\ 
  119818 & 119818 & 3 & 3 & -0.25 & -0.25 & -0.11 & -0.04 & -0.50 & -0.54 & 28.44 & -0.03 \\ 
  146301 & 146301 & 1 & 0 & 0.14 & 0.26 & 498188.34 & 0.28 & 0.56 & 0.37 & 0.60 & 0.52 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Missing meta-analysis pooled treatment effect and adjusted treatment effects
             of Figure 
ef{fig:adjustment.size}. Abbreviations are used for z-score (z) and Hedges g (g)} 
\label{missing.differences}
\end{table}

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Thu Jun 27 15:12:39 2019
\begin{table}[ht]
\centering
\begingroup\scriptsize
\begin{tabular}{lcccccc}
  \hline
 & 5\% & 25\% & 50\% & 75\% & 95\% & mean \\ 
  \hline
z-score: Fixed - Copas & -0.05 & -0.01 & 0.00 & 0.01 & 0.05 & 402.37 \\ 
  z-score: Random - Copas & -0.04 & 0.00 & 0.00 & 0.00 & 0.01 & 159.98 \\ 
  z-score: Fixed - Regression & -0.15 & -0.05 & -0.01 & 0.04 & 0.13 & -0.01 \\ 
  z-score: Random - Regression & -0.18 & -0.07 & -0.02 & 0.03 & 0.16 & -0.02 \\ 
  Hedges g: Fixed - Copas & -0.09 & -0.01 & 0.00 & 0.01 & 0.05 & -0.02 \\ 
  Hedges g: Random - Copas & -0.14 & 0.00 & 0.00 & 0.00 & 0.00 & -0.04 \\ 
  Hedges g: Fixed - Regression & -0.39 & -0.13 & -0.04 & 0.04 & 0.24 & -0.05 \\ 
  Hedges g: Random - Regression & -0.43 & -0.17 & -0.05 & 0.03 & 0.23 & -0.07 \\ 
  Log hazard ratio: Fixed - Copas & -0.02 & -0.00 & 0.00 & 0.00 & 0.03 & 0.01 \\ 
  Log hazard ratio: Random - Copas & -0.00 & 0.00 & 0.00 & 0.00 & 0.03 & 0.01 \\ 
  Log hazard ratio: Fixed - Regression & -0.15 & -0.01 & 0.07 & 0.14 & 0.21 & 0.06 \\ 
  Log hazard ratio: Random - Regression & -0.15 & -0.03 & 0.07 & 0.15 & 0.23 & 0.06 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Quantiles and Means of the differences between meta-analysis pooled treatment effects and small study adjusted treatment effects. The row names indicate which outcome measure, meta-analysis and adjustment method is used} 
\label{adjustment.difference}
\end{table}

@@

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-18-1}

@@

% %Chunck 6
% meta.bin <- meta.bin %>%ungroup() %>%  mutate(tes.d.schwarzer = ifelse(tes.d.test == schwarzer.test, "agree", "disagree"),
%                                               tes.d.peter = ifelse(tes.d.test == peter.test, "agree", "disagree"),
%                                               tes.d.rucker = ifelse(tes.d.test == rucker.test, "agree", "disagree"),
%                                               tes.d.harbord = ifelse(tes.d.test == harbord.test, "agree", "disagree"),
% agreement.bin <- meta.bin %>% ungroup() %>% summarise(tes.d.schwarzer = sum(tes.d.schwarzer == "agree")/n(),
